Dirac neutrino mass generation from Majorana messenger

### 2019-09-17 draft.tex
mc

\appendix
\section{Anomaly cancellation}
We use $f$ ($f$) to denote the general $\operatorname{U}(1)_X$ generation-independent charge assignments of the field $f_R$ ($F_L$). The three linear anomalies in $\operatorname{U(1)_X}$~\cite{Campos:2017dgc}
\begin{align}
  \label{eq:anolin}
  \left[\mathrm{SU}(3)_{c}\right]^{2} \mathrm{U}(1)_{X} :& &
[3 u+3 d]-[3 \cdot 2 q]=&0 \nonumber\\
\left[\mathrm{SU}(2)_{L}\right]^{2} \mathrm{U}(1)_{X} :&&
-[2 l+3 \cdot 2 q]=&0 \nonumber\\
\left[\mathrm{U}(1)_{Y}\right]^{2} \mathrm{U}(1)_{X} :&&
{ \left[(-2)^{2} e+3\left(\tfrac{4}{3}\right)^{2} u+3\left(-\tfrac{2}{3}\right)^{2} d\right]-\left[2(-1)^{2} l+3 \cdot 2\left(\tfrac{1}{3}\right)^{2} q\right]}=&
 0
  \end{align}
allows to express three $X$-charges in terms of the other two
\begin{align}
  u=&-e+\frac{2l}{3}\,,& d=& e-\frac{4l}{3}\,,& q=& -\frac{l}{3}\,.
\end{align}
The quadratic anomaly condition is automatically satisfied, while the mixed gauge-gravitational and cubic anomalies depend of any extra singlet quiral fermions of zero hypercharge, like the right-handed counterpart of the Dirac neutrinos. For $N$ extra quiral fields with $X$-charge $n_{\alpha}$, these conditions read
\begin{align}
  \left[\text{Grav}\right]^{2} \mathrm{U}(1)_{X}:\ \sum_{\alpha=1}^N n_{\alpha}+3 (e-2l)=&0\,, &  \left[\mathrm{U}(1)_{X}\right]^{3}:\ \sum_{\alpha=1}^N n_{\alpha}^3+3 (e-2l)^3=&0\,. &
\end{align}
We choose the solutions for with $\lambda\equiv e-2l$, such that
\begin{align}
  \label{eq:anolam}
  \sum_{\alpha=1}^{n} n_{\alpha}=&-3 \lambda\,,   & \sum_{\alpha=1}^{n} n_{\alpha}^3=&-3 \lambda^3\,, 
\end{align}
The full set of standard model charges in terms of two parameters~\cite{Appelquist:2002mw,Campos:2017dgc} that we chhose as $l$ and $\lambda$, is just
\begin{align}
  u=&-\lambda-\frac{4l}{3}\,,&d=&\lambda+\frac{2l}{3}\,,&q=&-\frac{l}{3}\,,&e=&\lambda+2l\,,&h=&-\lambda-l\,.
  \label{Eq:SMCharges}
\end{align}
If we now change $f\to  f/\lambda$, such that $\lambda\to 1$, the first of anomaly cancellation~\eqref{eq:anolin} remain invariant, and whithout lost of generality
always is possible to normalize the solutions such that the last set~\cite{eq:anolam} is just
\begin{align}
  \label{eq:anolamnor}
   \sum_{\alpha=1}^{n} n_{\alpha}=&-3\,,   & \sum_{\alpha=1}^{n} n_{\alpha}^3=&-3\,.
\end{align}
For example, the solution with $\lambda=3$ $n_{\alpha}=\left( -2,-2,-4,-1 \right)$~\cite{Appelquist:2002mw} can be easily normalized to the form \eqref{eq:anolamnor} with $n_{\alpha}\to n_{\alpha}/3$ as used in~\cite{Patra:2016ofq}. We work with the normalized solution in terms of a single parameter~\cite{Jenkins:1987ue,Oda:2015gna,Okada:2018tgy}, that we choose to be $l$, as summarized in column $\operatorname{U}(1)_X$ of Table~\ref{tab:partcont3}. In particular, this includes the solution  $n_{\alpha}=(-4,-4,+5)$~\cite{Appelquist:2002mw}.

>>>>

\appendix
\section{Anomaly cancellation}
We use $f$ ($f$) to denote the general $\operatorname{U}(1)_X$ generation-independent charge assignments of the field $f_R$ ($F_L$). The three linear anomalies in $\operatorname{U(1)_X}$~\cite{Campos:2017dgc}
\begin{align}
  \label{eq:anolin}
  \left[\mathrm{SU}(3)_{c}\right]^{2} \mathrm{U}(1)_{X} :& &
[3 u+3 d]-[3 \cdot 2 q]=&0 \nonumber\\
\left[\mathrm{SU}(2)_{L}\right]^{2} \mathrm{U}(1)_{X} :&&
-[2 l+3 \cdot 2 q]=&0 \nonumber\\
\left[\mathrm{U}(1)_{Y}\right]^{2} \mathrm{U}(1)_{X} :&&
{ \left[(-2)^{2} e+3\left(\tfrac{4}{3}\right)^{2} u+3\left(-\tfrac{2}{3}\right)^{2} d\right]-\left[2(-1)^{2} l+3 \cdot 2\left(\tfrac{1}{3}\right)^{2} q\right]}=&
 0
  \end{align}
allows to express three $X$-charges in terms of the other two
\begin{align}
  u=&-e+\frac{2l}{3}\,,& d=& e-\frac{4l}{3}\,,& q=& -\frac{l}{3}\,.
\end{align}
The quadratic anomaly condition is automatically satisfied, while the mixed gauge-gravitational and cubic anomalies depend of any extra singlet quiral fermions of zero hypercharge, like the right-handed counterpart of the Dirac neutrinos. For $N$ extra quiral fields with $X$-charge $n_{\alpha}$, these conditions read
\begin{align}
  \left[\text{Grav}\right]^{2} \mathrm{U}(1)_{X}:\ \sum_{\alpha=1}^N n_{\alpha}+3 (e-2l)=&0\,, &  \left[\mathrm{U}(1)_{X}\right]^{3}:\ \sum_{\alpha=1}^N n_{\alpha}^3+3 (e-2l)^3=&0\,. &
\end{align}
We choose the solutions with $\lambda\equiv e-2l$, such that
\begin{align}
  \label{eq:anolam}
  \sum_{\alpha=1}^{n} n_{\alpha}=&-3 \lambda\,,   & \sum_{\alpha=1}^{n} n_{\alpha}^3=&-3 \lambda^3\,, 
\end{align}
The full set of standard model charges in terms of two parameters~\cite{Appelquist:2002mw,Campos:2017dgc} that we choose as $l$ and $\lambda$, is just
\begin{align}
  u=&-\lambda-\frac{4l}{3}\,,&d=&\lambda+\frac{2l}{3}\,,&q=&-\frac{l}{3}\,,&e=&\lambda+2l\,,&h=&-\lambda-l\,.
  \label{Eq:SMCharges}
\end{align}
If we now change $f\to  f/\lambda$, such that $\lambda\to 1$, the first of anomaly cancellation~\eqref{eq:anolin} remain invariant, and without lost of generality
always is possible to normalize the solutions such that the last set~\eqref{eq:anolam} is just
\begin{align}
  \label{eq:anolamnor}
   \sum_{\alpha=1}^{n} n_{\alpha}=&-3\,,   & \sum_{\alpha=1}^{n} n_{\alpha}^3=&-3\,.
\end{align}
For example, the solution with $\lambda=3$: $n_{\alpha}=\left( -2,-2,-4,-1 \right)$~\cite{Appelquist:2002mw} can be easily normalized to the form \eqref{eq:anolamnor} with $n_{\alpha}\to n_{\alpha}/3$ as used in~\cite{Patra:2016ofq}. We work with the normalized solution in terms of a single parameter~\cite{Jenkins:1987ue,Oda:2015gna,Okada:2018tgy}, that we choose to be $l$, as summarized in column $\operatorname{U}(1)_X$ of Table~\ref{tab:partcont3}. In particular, this includes the solution  $n_{\alpha}=(-4,-4,+5)$~\cite{Appelquist:2002mw}.
